Testing and Isolation Efficacy; Insights from a Simple Epidemic Model

### 2020-12-03 SIR_manuscript.tex
panel plot update
Intro updated

@@

[comments about the figure:]
1- use a single legend, change the range manually.
\begin{figure}[h!]
\centering
\begin{subfigure}[t]{.45\textwidth}
\centering
\includegraphics[width=\linewidth]{./pix/R0contour_random.png}
\caption{}\label{p.a}
\end{subfigure}
%
\begin{subfigure}[t]{.45\textwidth}
\centering
\includegraphics[width=\linewidth]{./pix/R0contour_TTI.png}
\caption{}\label{p.b}
\end{subfigure}
\caption{Behaviour of the basic reproduction number, $\Rnum$, with respect to changes in the underlying parameters; remind the reader about the parameters and their values in this simulations. the solid line in each panel represents the critical contour of $\Rnum=1$.}
\label{pan}
\end{figure}

>>>>

There is useful comment from Troy Gayle [?, Ben?] on the purposes of testing:"The importance of the relative roles of at least four different, and sometimes conflicting, purposes of testing: (i) diagnosis and treatment, (ii) screening people for access to things like flights, surgery, LTCs etc, (iii) surveillance, and (iv) mitigation and control of disease spread." In this context, the random testing, the simplest form of testing strategy, is typically carried out for the purpose of surveillance. It is notable that, by random testing we mainly refer to PCR test given that there is almost negligable virological testing for survilance purposes. Furthermore, all of the accessible testing data is being used for one of the other three purposes rather than surveillance. These are non-random testing strategies with a different bios. Specifically, when the purpose is "(i) diagnosis and treatment" or "(iv) mitigation and control of disease spread", the bios is towards infectious individuals more strongly for (i) than (iv). When people are tested for "(ii) screening", the bios is towards the group-specific charactristics [I am making this up for now!]. For example, people who are getting on flights may/will be more mobile than people awaiting for a surgery and are probably going to stay in long-term care homes and consequently more isolated to begin with.

@@

[comments about the figure:]
1- use a single legend, change the range manually.
\begin{figure}[h!]
\centering
\begin{subfigure}[t]{.45\textwidth}
\centering
\includegraphics[width=\linewidth]{./pix/R0contour_random.pdf}
\caption{}\label{p.a}
\end{subfigure}
%
\begin{subfigure}[t]{.45\textwidth}
\centering
\includegraphics[width=\linewidth]{./pix/R0contour_TTI.pdf}
\caption{}\label{p.b}
\end{subfigure}
\caption{Behaviour of the basic reproduction number, $\Rnum$, with respect to changes in the underlying parameters; remind the reader about the parameters and their values in this simulations. the solid line in each panel represents the critical contour of $\Rnum=1$.}
\label{pan}
\end{figure}
